Woah cool a proper git paper!

### 2021-11-19 main.Rmd
Fix

---
title: "Woah cool a proper git paper!"
author: "Ryan, Brown, & Platt"
date: `r format(Sys.Date() + lubridate::years(20),"%A, %B %d, %Y")`
output: bookdown::pdf_document2
toc: yes
bibliography: references.bib
csl: aag.csl
---

@@

@@

>>>>

---
title: "Woah cool a proper git paper!"
author: "Ryan, Brown, & Platt"
date: "`r format(Sys.Date() + lubridate::years(20),'%A, %B %d, %Y')`"

# Using bookdown makes some things easier, like the \@ref() calls to figures and tables.
output: bookdown::pdf_document2

# Show table of contents?
toc: yes

bibliography: references.bib

# If we don't use AAG, we'll need to change this
csl: aag.csl
---

@@

You can call data from the main .Rmd from child files! Neat. Let's use this for mapping etc. -- for testing purposes we should define data in each section .Rmd to make things easier, but for the paper itself it'd be noice to only do that once in main.Rmd

@@

You can use `\@ref(fig:name-of-code-chunk)` to get the figure/table number, rather than manually entering "figure 2, 3, etc." It just outputs the number of the figure.

You can link to Zotero and type `@andersen2021` etc. to enter a Zotero-compatible in-text citation.
